MS_CNuptake.Rmd

### 2022-10-24 MS_CNuptake.Rmd
explain ISAM unit

#ISAM
#(given in kgC m-2 month-1 - they might not need to multiply with 12
#cdo seltimestep,127/156 ISAM_S2_fNup.nc a1.nc
#cdo -O timmean a1.nc ISAM_S2_fNup_ANN_mean.nc

@@

# The values multiply here is for unit from kg/m2/month to g/m2/yr (1000 for kg to g, and 31556952 from 1/second to 1/year)
ISAM_fNup$fNup<- ISAM_fNup$fNup*1000*31556952

>>>>

#ISAM
#basing on below cdo code
#cdo seltimestep,127/156 ISAM_S2_fNup.nc a1.nc
#cdo -O timmean a1.nc ISAM_S2_fNup_ANN_mean.nc

@@

# The values multiply here is for unit from kg/m2/s to g/m2/yr (1000 for kg to g, and 31556952 from 1/second to 1/year)
ISAM_fNup$fNup<- ISAM_fNup$fNup*1000*31556952
